---
title: "SIW4 Part 1:Simulation Exercize"
author: "Pratik Patil"
date: "17/10/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r DataLoading, include=FALSE}
## Loading Libraries
library("data.table")
library("ggplot2")
```

##Setting values

```{r Stuff}
set.seed(31) # set seed for reproducability
lam <- 0.2 # lambda=0.2
x <- 40 #samples=40
sim <- 1000 #simulations=1000
sim_exp <- replicate(sim, rexp(x, lam)) # simulate
mean_exp <- apply(sim_exp, 2, mean) # calculate mean of exponentials
```

## Question 1
Show where the distribution is centered at and compare it to the theoretical center of the distribution.

```{r}
ana_mean <- mean(mean_exp)
ana_mean
```

```{r}
# analytical mean
th_mean <- 1/lam
th_mean
```

```{r}
# visualization
hist(mean_exp, xlab = "mean", main = "Exponential Function Simulations")
abline(v = ana_mean, col = "blue")
abline(v = th_mean, col = "red")
```

The analytics mean is 4.993867 the theoretical mean 5. The center of distribution of averages of 40 exponentials is very close to the theoretical center of the distribution.

## Question 2

Show how variable it is and compare it to the theoretical variance of the distribution.. 

```{r}
# standard deviation of distribution
stan_dev_dist <- sd(mean_exp)
stan_dev_dist
```

```{r}
# standard deviation from analytical expression
stan_dev_th <- (1/lam)/sqrt(x)
stan_dev_th
```

```{r}
# variance of distribution
var_dist <- stan_dev_dist^2
var_dist
```

```{r}
# variance from analytical expression
var_th <- ((1/lam)*(1/sqrt(x)))^2
var_th
```

Standard Deviation of the distribution is 0.7931608 with the theoretical SD calculated as 0.7905694. The Theoretical variance is calculated as ((1 / ??) * (1/???n))<sup>2</sup> = 0.625. The actual variance of the distribution is 0.6291041

## Question 3
Show that the distribution is approximately normal.

```{r}
xf <- seq(min(mean_exp), max(mean_exp), length=100)
yf <- dnorm(xf, mean=1/lam, sd=(1/lam/sqrt(x)))
hist(mean_exp,breaks=x,prob=T,col="red",xlab = "means",main="Density of means",ylab="density")
lines(xf, yf, pch=22, col="orange", lty=5)
```

```{r}
# compare the distribution of averages of 40 exponentials to a normal distribution
qqnorm(mean_exp)
qqline(mean_exp, col = 2)
```

Due to Due to the central limit theorem (CLT), the distribution of averages of 40 exponentials is very close to a normal distribution.
