---
title: 'SWI4 Part 2:'
author: "Pratik Patil"
date: "17/10/2020"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

We are going to analyze the ToothGrowth data in the R datasets package.

Question 1:  
Load the ToothGrowth data and perform some basic exploratory data analyses

Plot the length against the dose for each of the supplements.
In order to gain a better view of growth rates, we also add a curve.
It is seen that the growth rates seem to behave differently for both supplements.

```{r warning=F}
library(ggplot2)
data(ToothGrowth)
qplot(dose, len, data=ToothGrowth, facets=.~supp, geom=c("point", "smooth"), method="loess")
```

Question 2:  
Provide a basic summary of the data.

This dataset contains three variables: supplement, dose and len.
For each supplement, and each dose we calculate basic descriptive statistics:
standard deviation, variance, and mean.

```{r}
dose <- as.numeric(levels(as.factor(ToothGrowth$dose)))
supp <- levels(ToothGrowth$supp)
# Structured for further processing
ls <- list()
y <- Map(function(s) {
  Map(function(d) {
    l <- ToothGrowth$len[ToothGrowth$dose == d & ToothGrowth$supp == s]
    ls <<- rbind(ls, list(supp = s, dose = d, sd=sd(l), var=var(l), mu=mean(l)))
  }, dose)
}, supp)
ls
```

Question 3:  
Use confidence intervals and hypothesis tests to compare tooth growth by supp and dose. (Use the techniques from class even if there's other approaches worth considering)

We perform the student-t test for each dose level between the two supplements:

```{r}
tt = list()
for (d in dose) {
  ojd <- ToothGrowth$len[ToothGrowth$dose == d & ToothGrowth$supp == "OJ"]
  vcd <- ToothGrowth$len[ToothGrowth$dose == d & ToothGrowth$supp == "VC"]
  t <- t.test(ojd, vcd, var.equal=T)
  id <- paste("OJ", d, "-", "VC", d)
  tt <- rbind(tt, list(id=id, p.value=t$p.value, ci.lo=t$conf.int[1], ci.hi=t$conf.int[2]))
}
tt
```

Question 4:  
State your conclusions and the assumptions needed for your conclusions.

Assumption:  
1.We assume that variance in all groups should be expected to be equal.
2.The underlying assumption is that sampling of Guinea Pigs to assign them to a supplement and a dose was done properly.

Conclusions:  
Observing the test results from the other questions we can **reject** the following hypotheses:

1. True difference in means between OJ 0.5 and VC 0.5 is equal to 0
2. True difference in means between OJ 1 and VC 1 is equal to 0
3. True difference in means between OJ 2 and VC 2 is equal to 0